---
title: "How Charter Schools Affect Nearby Public Schools"
author: 
- "Austin Sell"
- "Nicole Kovski"
date: "`r format(Sys.time(), '%B %d, %Y')`"
abstract: "Abstract..."
output:
    pdf_document
fontsize: 12pt
geometry: margin=1in
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

---
references:
- id: Ochoa2006
  title: "TV Watching Modifies Obesity Risk Linked to the 27Glu Polymorphism of the ADRB2 Gene in Girls"
  author:
  - family: Ochoa
    given: MC
  - family: Moreno-Aliaga
    given: MJ
  - family: Martinez-Gonzalez
    given: MA
  - family: Martinez
    given: JA
  - family: Marti
    given: A
  container-title: Pediatric Obesity
  volume: 1
  issue: 2
  page: 83-88
  type: article-journal
  issued:
    year: 2006
    
- id: Danner2008
  title: "A National Longitudinal Study of the Association between Hours of TV Viewing and the Trajectory of BMI Growth among US Children"
  author:
  - family: Danner
    given: Fred W
  container-title: "Journal of Pediatric Psychology"
  volume: 33
  issue: 10
  page: 1100-1107
  type: article-journal
  issued:
    year: 2008
    
- id: Rey2008
  title: "Sedentary Behaviour and Obesity Development in Children and Adolescents"
  author:
  - family: Rey-Lopez
    given: Juan Pablo
  - family: Vicente-Rodriguez
    given: German
  - family: Biosca
    given: Mireia
  - family: Moreno
    given: Luis A.
  container-title: "Nutrition, Metabolism and Cardiovascular Diseases"
  volume: 18
  issue: 3
  page: 242-251
  type: article-journal
  issued:
    year: 2008
  
...
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(foreign)
library(nlme)      # Estimation of mixed effects models
library(lme4)      # Alternative package for mixed effects models
library(plm)       # Econometrics package for linear panel models
library(arm)       # Gelman & Hill code for mixed effects simulation
library(pcse)      # Calculate PCSEs for LS models (Beck & Katz)
library(tseries)   # For ADF unit root test
library(simcf)     # For panel functions and simulators
library(MASS)

data <- read.dta("Data/CharterInfoSetAnalysis.dta")

# SURVEYYEAR = year
# SCHOOLIDNCESASSIGNED = school id
# TOTALSTUDENTS = total students
# charteronehalfoverlap = charter school with 1.5 miles with overlapping grades
# chartertwohalfoverlap = charter school with 2.5 miles with overlapping grades
# charterfiveoverlap = charter school with 5 miles with overlapping grades
# chartertenoverlap = charter school with 10 miles with overlapping grades
# numchartersonehalfoverlap = total number of charters within 1.5 miles with overlapping grades
# numcharterstwohalfoverlap = total number of charters within 2.5 miles with overlapping grades
# numchartersfiveoverlap = total number of charters within 5 miles with overlapping grades
# numcharterstenoverlap = total number of charters within 10 miles with overlapping grades
# FRLpercent = percent of enrollment that is FRL eligible
# BLACKpercent = percent of enrollment that is black
# HISPANICpercent = percent of enrollment that is hispanic
# WHITEpercent = percent of enrollment that is white
# AGENCYNAMEDISTRICT = school district name
# SCHOOLNAME = school name

## rename variables
data$id <- data$SCHOOLIDNCESASSIGNED
data$year <- data$SURVEYYEAR

# data <- subset(data, data$AGENCYNAMEDISTRICT=="OKLAHOMA CITY" | data$AGENCYNAMEDISTRICT=="TULSA")


## create lags
DVs <- list(data$FRLpercent, data$BLACKpercent, data$HISPANICpercent, data$WHITEpercent, data$TOTALSTUDENTS)

data$FRLlag1 <- lagpanel(data$FRLpercent, data$id, data$year,1)
data$BLACKlag1 <- lagpanel(data$BLACKpercent, data$id, data$year,1)
data$HISPANIClag1 <- lagpanel(data$HISPANICpercent, data$id, data$year,1)
data$HISPANIClag2 <- lagpanel(data$HISPANICpercent, data$id, data$year,2)
data$HISPANIClag3 <- lagpanel(data$HISPANICpercent, data$id, data$year,3)
data$WHITElag1 <- lagpanel(data$WHITEpercent, data$id, data$year,1)
data$TOTALSTUDENTSlag1 <- lagpanel(data$TOTALSTUDENTS, data$id, data$year,1)

## model for total students

selectdata <- na.omit(cbind(data$id,
                            data$year,
                            data$TOTALSTUDENTS,
                            data$TOTALSTUDENTSlag1,
                            data$charteronehalfoverlap,
                            data$chartertwohalfoverlap,
                            data$charterfiveoverlap,
                            data$chartertenoverlap,
                            data$numchartersonehalfoverlap,
                            data$numcharterstwohalfoverlap,
                            data$numchartersfiveoverlap,
                            data$numcharterstenoverlap,
                            data$HISPANICpercent,
                            data$HISPANIClag1,
                            data$FRLpercent,
                            data$FRLlag1,
                            data$WHITEpercent,
                            data$WHITElag1,
                            data$BLACKpercent,
                            data$BLACKlag1))

selectdata <- as.data.frame(selectdata)
names(selectdata) <- c("id",
                       "year",
                       "totalstudents",
                       "totalstudentslag1",
                       "charteronehalfoverlap",
                       "chartertwohalfoverlap",
                       "charterfiveoverlap",
                       "chartertenoverlap",
                       "numchartersonehalfoverlap",
                       "numcharterstwohalfoverlap",
                       "numchartersfiveoverlap",
                       "numcharterstenoverlap",
                       "HISPANICpercent",
                       "HISPANIClag1",
                       "FRLpercent",
                       "FRLlag1",
                       "WHITEpercent",
                       "WHITElag1",
                       "BLACKpercent",
                       "BLACKlag1")

attach(selectdata)

```

```{r}
## PLM data frame

pdata <- pdata.frame(selectdata, index=c("id", "year"))

# ALL MODELS

DV <- list(FRLpercent, HISPANICpercent, BLACKpercent, WHITEpercent)
DVlag <- list(FRLlag1, HISPANIClag1, BLACKlag1, WHITElag1)
charter <- list(charteronehalfoverlap, chartertwohalfoverlap, charterfiveoverlap, chartertenoverlap)

femodel1.5 <- NULL
femodel2.5 <- NULL
femodel5 <- NULL
femodel10 <- NULL

femodels <- list(femodel1.5, femodel2.5, femodel5, femodel10)

for (i in 1:length(DV)){
  for (j in 1:length(charter)){
    femodels[[j]][[i]] <- plm(DV[[i]] ~ DVlag[[i]] + charter[[j]],
                              data = pdata, model = "within")
  }
}

fetemodel1.5 <- NULL
fetemodel2.5 <- NULL
fetemodel5 <- NULL
fetemodel10 <- NULL
fetemodels <- list(fetemodel1.5, fetemodel2.5, fetemodel5, fetemodel10)

for (i in 1:length(DV)){
  for (j in 1:length(charter)){
    femodels[[j]][[i]] <- plm(DV[[i]] ~ DVlag[[i]] + charter[[j]] + factor(year),
                              data = pdata, model = "within")
  }
}

#random effects model - 5 miles
fit.r1 <- lme(fixed = totalstudents ~ charterfiveoverlap + factor(year),
            random = ~ 1 | id,
            correlation = corARMA(form = ~ year | id,
                                  p = 1,
                                  q = 0))
summary(fit.r1)

## fixed effects model - 5 miles
pvar(pdata)

fit.f1 <- plm(FRLpercent ~ FRLlag1 + chartertenoverlap,
              data=pdata, model="within")
summary(fit.f1)

fit.f2 <- plm(HISPANICpercent ~ HISPANIClag1 + chartertenoverlap,
              data=pdata, model="within")

fit.f3 <- plm(BLACKpercent ~ BLACKlag1 + chartertenoverlap,
              data=pdata, model="within")

fit.f4 <- plm(WHITEpercent ~ WHITElag1 + chartertenoverlap,
              data=pdata, model="within")
```

\pagebreak

# Introduction


# Background and Theory


# Data


# Methods


# Results


# Conclusion